---
title: "Data QCQA"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(datasets)
library(flexdashboard)
library(shiny)
library(dplyr)
library(plotly)
library(ggplot2)
library(ggpubr)
library(forecast)
library(lubridate)
library(hms)
library(gridExtra)
library(amerifluxr)
library(heatmaply)
library(data.table)
library(ggpmisc)
library(knitr)
```

<!-- Load ini file -->
```{r echo=FALSE, include=FALSE}
source(file)
```

Sonic data 
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Sonic variables and diagnostics

```{r}
sonic_plots(data,vars_WS,vars_WD,vars_other_sonic,units_other_sonic,pitch_ind)
```

Column {data-width=400}
-----------------------------------------------------------------------

### mean wind speed vs. u*
```{r}
scatter_plot_QCQA(data,vars_WS[1],vars_other_sonic[1],
                  "WS (m/s)","USTAR (m/s)",0)
```

### sigma_w vs. u*
```{r}
scatter_plot_QCQA(data,vars_other_sonic[1],
                  wind_std,
                  "USTAR (m/s)","W_SIGMA (m/s)",0)
```

Temp/RH 
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Air and RH temperature comparison 
```{r}
temp_RH_data_plotting(data,vars_temp,vars_RH)
```

Column {data-width=400}
-----------------------------------------------------------------------

### Temperature scatterplot
```{r}
scatter_plot_QCQA(data,vars_temp[1],vars_temp[2],vars_temp[1],vars_temp[2],0)
```

### RH HMP vs. RH 7200

```{r}
scatter_plot_QCQA(data,vars_RH[1],vars_RH[2], vars_RH[1],vars_RH[2],0)
```

Rad Time Series 
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Radiation timeseries  
```{r}
radiation_data_plotting(data,vars_radiometer,vars_NETRAD,vars_PPFD,var_potential_rad)
```

Column {data-width=400}
-----------------------------------------------------------------------

### SW_IN vs PPDF_IN
```{r}
scatter_plot_QCQA(data,vars_radiometer[1],vars_PPFD[1], vars_radiometer[1],vars_PPFD[1],0)
```

### SW_IN vs PPDF_IN R2 and Slope

```{r}
R2_slope_QCQA(data,vars_radiometer[1],vars_PPFD[1])
```

Rad Diagnostics
=======================================================================

Row 
-----------------------------------------------------------------------

### Checking for offsets between SW_IN (blue) and potential radiation (red)  
```{r}
# Compute mean diurnal pattern for 15 day moving window
diurnal.composite <- diurnal.composite.rad(data,var_potential_rad,vars_radiometer[1],vars_PPFD[1],15,48)
diurnal.composite <- diurnal.composite[is.finite(diurnal.composite$potential_radiation), ]

SWIN_vs_potential_rad(diurnal.composite)
```

### Cross between SW_IN and potential radiation
```{r}
p <- xcorr_rad(diurnal.composite)
toWebGL(p[[1]])
```

Row 
------------------------------------------------------------------------

### Checking for offsets between PPFD_IN (green) and potential radiation (red)  
```{r}
PPFDIN_vs_potential_rad(diurnal.composite)
```

### Cross correlation analysis between PPDF_IN and potential radiation
```{r}
p <- xcorr_rad(diurnal.composite)
toWebGL(p[[2]])
```

Pressure 
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Pressure 
```{r}
# Barometric pressure 
plotly_loop(data,vars_pressure,"Barometric pressure (kPa)")
```

Column {data-width=400}
-----------------------------------------------------------------------

### Pressure comparison (Met PA vs EC PA)
```{r}
scatter_plot_QCQA(data,vars_pressure[1],vars_pressure[2], vars_pressure[1],vars_pressure[2],0)
```

Met time series
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
selectInput('y', 'Variable', names(data[, !names(data) %in% c("datetime")])) 
```

Column
-----------------------------------------------------------------------

### Time series of single met variable

```{r}
dataset <- reactive({
  data[, c(input$x, input$y)]
})

renderPlotly({
  plot_ly(data, x = ~datetime, y = ~data[[input$y]], type = 'scatter', mode = 'lines') %>%
    layout(yaxis = list(title = input$y)) %>%
    toWebGL() 
})
```

Met diurnal pattern
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
selectInput('z', 'Variable', names(data[, !names(data) %in% c("datetime")])) 
```

Column
-----------------------------------------------------------------------

### Diurnal pattern of single met variable

```{r}

dataset <- reactive({
  diurnal.summary(data, input$z, 30, 15)
  
})

renderPlotly({
  
  diurnal.summary.composite <- dataset() %>%
    group_by(firstdate,HHMM) %>%
    dplyr::summarize(var = median(var, na.rm = TRUE),
                     HHMM = first(HHMM))
  diurnal.summary.composite$time <- as.POSIXct(as.character(diurnal.summary.composite$HHMM), format="%R", tz="UTC")
  
  p <- ggplot() +
    geom_point(data = dataset(), aes(x = time, y = var),color = 'Grey',size = 0.1) +
    geom_line(data = diurnal.summary.composite, aes(x = time, y = var),color = 'Black') +
    scale_x_datetime(breaks="6 hours", date_labels = "%H") + ylab(input$z)
  p <- ggplotly(p+ facet_wrap(~as.factor(firstdate))) %>% toWebGL()
  p
  
})
```

Flux time series 
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
selectInput('f', 'Variable', flux_vars) 

if (exists("data_thirdstage") == TRUE) {
  selectInput('f3', 'Gap-filled Variable', flux_vars_gf) 
}
```

Column
-----------------------------------------------------------------------

### Time series of single flux variable

```{r}

dataset_flux <- reactive({
  data[, c("datetime", input$f)]
})

if (exists("data_thirdstage") == TRUE) {
  
  dataset_thirdstage <- reactive({
    data_thirdstage[, c(input$f3)]
  })
}

renderPlotly({
  
  colors = c("gap-filled" = "black", "Second stage" = rgb(0.2, 0.6, 0.9, 1), "Third stage" = "#69b3a2")
  
  if (exists("data_thirdstage") == TRUE) {
    
    df <- cbind(dataset_flux(), dataset_thirdstage(),data_thirdstage[, input$f])
    colnames(df) <- c("datetime","gap_filled","second_stage","third_stage")
    
    p <- ggplot(data = df) +
      geom_line(aes_string(x = "datetime", y = "gap_filled",color = shQuote("Gap-filled")))+
      geom_line(aes_string(x = "datetime", y = "second_stage", color = shQuote("Second stage")))+
      geom_line(aes_string(x = "datetime", y = "third_stage", color = shQuote("Third stage")))+
      xlab("") + ylab(input$f) +
      scale_color_manual(values = colors) + labs(color = "Trace")
    p <- ggplotly(p) %>% toWebGL()
    
  } else {
    
    df <- cbind(dataset_flux())
    colnames(df) <- c("datetime","second_stage")
    
    p <- ggplot(data = df) +
      geom_line(aes_string(x = "datetime", y = "second_stage", color = shQuote("Second stage")))+
      xlab("") + ylab(input$f) +
      scale_color_manual(values = colors) + labs(color = "Trace")
    p <- ggplotly(p) %>% toWebGL()}
  
})

```

Flux summary
=======================================================================

```{r}
if (exists("data_thirdstage") == TRUE) {
  # Create conversion factors
  conv_factor <- data.frame(44.01/(10^6)*(60*30),16.04/(10^9)*(60*30),(60*30)/(10^6))
  colnames(conv_factor) <- c("CO2","CH4","Energy")
  
  # Create string for conversion factor variable names
  conv_factor_vars <- c("CO2","CH4","Energy")
}
```

Column {.sidebar}
-----------------------------------------------------------------------

```{r}

if (exists("data_thirdstage") == TRUE) {
  selectInput('fl3', 'Gap-filled Variable', flux_vars_gf) 
}
if (exists("data_thirdstage") == TRUE) {
  selectInput('conv', 'Conversion factor for cumulative flux', conv_factor_vars) 
}
```

Column {data-width=600}
-----------------------------------------------------------------------

### Daily mean time series of single flux variable by year (need stage 3 data)

```{r}

if (exists("data_thirdstage") == TRUE) {
  dataset_thirdstage_daily <- reactive({
    data_thirdstage[, c("year","DOY", input$fl3)]
  })
}

renderPlotly({
  
  if (exists("data_thirdstage") == TRUE) {
    
    df <- dataset_thirdstage_daily()
    colnames(df)[3] <- "var"
    
    daily.data <- df %>%
      group_by(year,DOY) %>%
      dplyr::summarize(var = median(var, na.rm = TRUE),
                       DOY = first(DOY),
                       year = as.factor(first(year)))
    
    p <- ggplot() +
      geom_line(data = daily.data , aes(x = DOY, y = var, color = year))+ 
      ylab(input$fl3)
    p <- ggplotly(p) %>% toWebGL()
  }
})
```

Column {data-width=400}
-----------------------------------------------------------------------

### Cumulative flux

```{r}

if (exists("data_thirdstage") == TRUE) {
  
  dataset_thirdstage_cum <- reactive({
    data_thirdstage[, c("year","DOY", input$fl3)]
  })
  
  convfactor <- reactive({
    conv_factor[ ,c(input$conv)]
  })
  
  renderPlotly({
    
    df <- dataset_thirdstage_cum()
    colnames(df)[3] <- "var"
    
    cf <- convfactor()
    
    daily.cum <- df %>%
      group_by(year,DOY) %>%
      dplyr::summarize(var = sum(var*cf), 
                       DOY = first(DOY),
                       year = as.factor(first(year)))
    daily.cum$var_cum <- cumsum(daily.cum$var)
    
    p <- ggplot() +
      geom_line(data = daily.cum, aes(x = DOY, y = var_cum, color = year))+ 
      ylab(input$fl3)
    p <- ggplotly(p) %>% toWebGL()
    
  })
}
```

### Mean diurnal pattern

```{r}

if (exists("data_thirdstage") == TRUE) {
  
  dataset_thirdstage_diurnal <- reactive({
    data_thirdstage[, c("datetime", input$fl3)]
  })
  
  renderPlotly({
    
    colname <- colnames(dataset_thirdstage_diurnal())
    var_in <-  str_split(colname[2],"_")
    
    df <- data_thirdstage[, c("datetime", var_in[[1]][1])]
    colnames(df)[2] <- "var"
    
    data.diurnal <- df %>%
      mutate(
        year = as.factor(year(datetime)),
        month = month(datetime),
        day = day(datetime),
        jday = yday(datetime),
        hour = hour(datetime),
        minute = minute(datetime),
        HHMM = format(as.POSIXct(datetime), format = "%H:%M")
      ) %>%  # Create hour and minute variable (HHMM)
      group_by(year, HHMM) %>%
      dplyr::summarize(var = median(var,na.rm = TRUE))
    
    data.diurnal$time <- as.POSIXct(as.character(data.diurnal$HHMM), format="%R", tz="UTC")
    
    p <- ggplot() +
      geom_line(data = data.diurnal, aes(x = time, y = var,color = year)) +
      scale_x_datetime(breaks="6 hours", date_labels = "%R") + ylab(var_in[[1]][1])
    
    p <- ggplotly(p) %>% toWebGL()
    p
    
  })
}
```

Flux diagnostics
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Flux diagnostics
```{r}
flux_diagnostic_plots(data,vars_flux_diag)
```

Column {data-width=400}
-----------------------------------------------------------------------

### EBC half-hourly
```{r}
scatter_plot_QCQA_EBC(data_thirdstage,vars_EBC_AE,c("H","LE"),"AE  (W m-2)","H+LE (W m-2)")
```

### EBC daily
```{r}
scatter_plot_QCQA_EBC_daily(data_thirdstage,vars_EBC_AE,c("H","LE"),"AE  (W m-2)","H+LE (W m-2)")
```
