---
title: "Data QCQA"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(datasets)
library(flexdashboard)
library(shiny)
library(dplyr)
library(plotly)
library(ggplot2)
library(ggpubr)
library(forecast)
library(lubridate)
library(hms)
library(gridExtra)
library(amerifluxr)
library(heatmaply)
library(data.table)
library(ggpmisc)
library(knitr)
```

<!-- Load ini file -->

```{r echo=FALSE, include=FALSE}
source(file)
```

# Sonic data

## Column {data-width="600"}

### Sonic variables and diagnostics

```{r}
sonic_plots(data,vars_WS,vars_WD,vars_other_sonic,units_other_sonic,pitch_ind)
```

## Column {data-width="400"}

### mean wind speed vs. u\*

```{r}
scatter_plot_QCQA(data,vars_WS[1],vars_other_sonic[1],
                  "WS (m/s)","USTAR (m/s)",0)
```

### sigma_w vs. u\*

```{r}
scatter_plot_QCQA(data,vars_other_sonic[1],
                  wind_std,
                  "USTAR (m/s)","W_SIGMA (m/s)",0)
```

# Temp/RH

## Column {data-width="600"}

### Air and RH temperature comparison

```{r}
temp_RH_data_plotting(data,vars_temp,vars_RH)
```

## Column {data-width="400"}

### Temperature scatterplot

```{r}
scatter_plot_QCQA(data,vars_temp[1],vars_temp[2],vars_temp[1],vars_temp[2],0)
```

### RH HMP vs. RH 7200

```{r}
scatter_plot_QCQA(data,vars_RH[1],vars_RH[2], vars_RH[1],vars_RH[2],0)
```

# Rad Time Series

## Column {data-width="600"}

### Radiation timeseries

```{r}
radiation_data_plotting(data,vars_radiometer,vars_NETRAD,vars_PPFD,var_potential_rad)
```

## Column {data-width="400"}

### SW_IN vs PPDF_IN

```{r}
scatter_plot_QCQA(data,vars_radiometer[1],vars_PPFD[1], vars_radiometer[1],vars_PPFD[1],0)
```

### SW_IN vs PPDF_IN R2 and Slope

```{r}
R2_slope_QCQA(data,vars_radiometer[1],vars_PPFD[1])
```

# Rad Diagnostics

## Column {.tabset .tabset-fade}

### SW_IN vs potential rad

```{r}
# Compute mean diurnal pattern for 15 day moving window
diurnal.composite <- diurnal.composite.rad(data,var_potential_rad,vars_radiometer[1],vars_PPFD[1],15,48)
diurnal.composite <- diurnal.composite[is.finite(diurnal.composite$potential_radiation), ]

SWIN_vs_potential_rad(diurnal.composite)
```

### PPFD_IN vs potential rad

```{r}
PPFDIN_vs_potential_rad(diurnal.composite)
```

## Column {.tabset .tabset-fade}

### Cross correlation SW_IN

```{r}
p <- xcorr_rad(diurnal.composite)
toWebGL(p[[1]])
```

### Cross correlation PPFD_IN

```{r}
p <- xcorr_rad(diurnal.composite)
toWebGL(p[[2]])
```

# Pressure

## Column {data-width="600"}

### Pressure

```{r}
# Barometric pressure 
plotly_loop(data,vars_pressure,"Barometric pressure (kPa)")
```

## Column {data-width="400"}

### Pressure comparison (Met PA vs EC PA)

```{r}
scatter_plot_QCQA(data,vars_pressure[1],vars_pressure[2], vars_pressure[1],vars_pressure[2],0)
```

# Time series

## Column {.sidebar}

```{r}
selectInput('y', 'Variable', names(data[, !names(data) %in% c("datetime")])) 
```

## Column

### Time series of single variable

```{r}
dataset <- reactive({
  data[, c(input$x, input$y)]
})

renderPlotly({
  plot_ly(data, x = ~datetime, y = ~data[[input$y]], type = 'scatter', mode = 'lines') %>%
    layout(yaxis = list(title = input$y)) %>%
    toWebGL() 
})
```

# Diurnal pattern

## Column {.sidebar}

```{r}
selectInput('z', 'Variable', names(data[, !names(data) %in% c("datetime")])) 
```

## Column

### Diurnal pattern of single variable

```{r}

dataset <- reactive({
  diurnal.summary(data, input$z, 30, 15)
  
})

renderPlotly({
  
  diurnal.summary.composite <- dataset() %>%
    group_by(firstdate,HHMM) %>%
    dplyr::summarize(var = median(var, na.rm = TRUE),
                     HHMM = first(HHMM))
  diurnal.summary.composite$time <- as.POSIXct(as.character(diurnal.summary.composite$HHMM), format="%R", tz="UTC")
  
  p <- ggplot() +
    geom_point(data = dataset(), aes(x = time, y = var),color = 'Grey',size = 0.1) +
    geom_line(data = diurnal.summary.composite, aes(x = time, y = var),color = 'Black') +
    scale_x_datetime(breaks="6 hours", date_labels = "%H") + ylab(input$z)
  p <- ggplotly(p+ facet_wrap(~as.factor(firstdate))) %>% toWebGL()
  p
  
})
```

# Flux time series

## Column {.sidebar}

```{r}
selectInput('f', 'Variable', flux_vars) 

if (exists("data_thirdstage") == TRUE) {
  selectInput('f3', 'Gap-filled Variable', flux_vars_gf) 
}
```

## Column

### Time series of single flux variable

```{r}

dataset_flux <- reactive({
  data[, c("datetime", input$f)]
})

if (exists("data_thirdstage") == TRUE) {
  
  dataset_thirdstage <- reactive({
    data_thirdstage[, c(input$f3)]
  })
}

renderPlotly({
  
  colors = c("Second stage" = "grey44", "Third stage" = rgb(0.2, 0.6, 0.9, 1), "Third stage gap-filled" = "#69b3a2")
  
  if (exists("data_thirdstage") == TRUE) {
    
    df <- cbind(dataset_flux(),data_thirdstage[, input$f],dataset_thirdstage())
    colnames(df) <- c("datetime","second_stage","third_stage","third_stage_gap_filled")
    
    p <- ggplot(data = df) +
      geom_line(aes_string(x = "datetime", y = "third_stage_gap_filled", color = shQuote("Third stage gap-filled")))+
      geom_line(aes_string(x = "datetime", y = "second_stage",color = shQuote("Second stage")))+
      geom_line(aes_string(x = "datetime", y = "third_stage", color = shQuote("Third stage")))+
      xlab("") + ylab(input$f) +
      scale_color_manual(values = colors) + labs(color = "Trace")
    p <- ggplotly(p) %>% toWebGL()
    
  } else {
    
    df <- cbind(dataset_flux())
    colnames(df) <- c("datetime","second_stage")
    
    p <- ggplot(data = df) +
      geom_line(aes_string(x = "datetime", y = "second_stage", color = shQuote("Second stage")))+
      xlab("") + ylab(input$f) +
      scale_color_manual(values = colors) + labs(color = "Trace")
    p <- ggplotly(p) %>% toWebGL()}
  
})
```

# Flux summary

```{r}
if (exists("data_thirdstage") == TRUE) {
  # Create conversion factors
  conv_factor <- data.frame(12.01/(10^6)*(60*30),12.01/(10^9)*(60*30),(60*30)/(10^6))
  colnames(conv_factor) <- c("CO2","CH4","Energy")
  
  # Create string for conversion factor variable names
  conv_factor_vars <- c("CO2","CH4","Energy")
  
  # Create labels for units
  conv_factor_units_cum <- data.frame("gC m-2","gC m-2","MJ m-2")
  colnames(conv_factor_units_cum) <- c("CO2","CH4","Energy")
  conv_factor_units_mean <- data.frame("umol CO2 m-2 s-1","nmol CH4 m-2 s-1","W m-2")
  colnames(conv_factor_units_mean) <- c("CO2","CH4","Energy")
}
```

## Column {.sidebar}

```{r}

if (exists("data_thirdstage") == TRUE) {
  selectInput('fl3', 'Gap-filled Variable', flux_vars_gf) 
}
if (exists("data_thirdstage") == TRUE) {
  selectInput('conv', 'Conversion factor for cumulative flux', conv_factor_vars) 
}
```

## Column {data-width="600"}

### Daily mean time series of single flux variable by year (need stage 3 data)

```{r}

if (exists("data_thirdstage") == TRUE) {
  dataset_thirdstage_daily <- reactive({
    data_thirdstage[, c("year","DOY", input$fl3)]
  })
  
  convfactor <- reactive({
    conv_factor[ ,c(input$conv)]
  })
  
  units <- reactive({
    conv_factor_units_cum[ ,c(input$conv)]
  })
}

renderPlotly({
  
  if (exists("data_thirdstage") == TRUE) {
    
    cf <- convfactor()
    units_cf <- units()
    
    df <- dataset_thirdstage_daily()
    colnames(df)[3] <- "var"
    
    daily.data <- df %>%
      group_by(year,DOY) %>%
      dplyr::summarize(var = sum(var*cf, na.rm = F),
                       DOY = first(DOY),
                       year = as.factor(first(year)))
    
    p <- ggplot() +
      geom_line(data = daily.data , aes(x = DOY, y = var, color = year))+ 
      ylab(paste0(input$fl3," (", units_cf," d-1)",sep = ""))
    p <- ggplotly(p) %>% toWebGL()
  }
})
```

## Column {data-width="400"}

### Cumulative flux (full yrs only)

```{r}

if (exists("data_thirdstage") == TRUE) {
  
  dataset_thirdstage_cum <- reactive({
    data_thirdstage[, c("year","DOY", input$fl3)]
  })
  
  convfactor <- reactive({
    conv_factor[ ,c(input$conv)]
  })
  
  units <- reactive({
    conv_factor_units_cum[ ,c(input$conv)]
  })
  
  renderPlotly({
    
    df <- dataset_thirdstage_cum()
    colnames(df)[3] <- "var"
    
    cf <- convfactor()
    units_cf <- units()
    
    # Determine which years are a full year of data
    nyrs <- unique(df$year)
    
    count_yr <- df %>% 
      group_by(year) %>%
      dplyr::summarize(count = sum(!is.na(var)))
    
    yrs <- nyrs[count_yr$count >=17520] # Greater or equal to 365 days (i.e. 17520 observations)
    
    df2 <- with(df,df[(year >= yrs[1] & year <= yrs[length(yrs)]),])
    
    daily.cum <- df2 %>%
      group_by(year,DOY) %>%
      dplyr::summarize(var = sum(var*cf), 
                       DOY = first(DOY),
                       year = as.factor(first(year)))
    daily.cum$var_cum <- cumsum(daily.cum$var)
    
    p <- ggplot() +
      geom_line(data = daily.cum, aes(x = DOY, y = var_cum, color = year))+ 
      ylab(paste0(input$fl3," (",units_cf,")",sep = ""))
    p <- ggplotly(p) %>% toWebGL()
    
  })
}
```

### Mean diurnal pattern (non gap-filled fluxes)

```{r}

if (exists("data_thirdstage") == TRUE) {
  
  dataset_thirdstage_diurnal <- reactive({
    data_thirdstage[, c("year","datetime", input$fl3)]
  })
  
  units <- reactive({
    conv_factor_units_mean[ ,c(input$conv)]
  })
  
  renderPlotly({
    
    # Determine which years are a full year of data
    df <- dataset_thirdstage_diurnal()
    colnames(df)[3] <- "var"
    
    nyrs <- unique(df$year)
    
    count_yr <- df %>% 
      group_by(year) %>%
      dplyr::summarize(count = sum(!is.na(var)))
    
    yrs <- nyrs[count_yr$count >=17520] # Greater or equal to 365 days (i.e. 17520 observations)
    
    colname <- colnames(dataset_thirdstage_diurnal())
    var_in <-  str_split(colname[3],"_")
    
    # Create data frame with non gap-filled third stage fluxes to compute mean diurnal pattern
    df_ngf <- data_thirdstage[, c("datetime", var_in[[1]][1])] # non gap-filled df
    colnames(df_ngf)[2] <- "var"
    
    units_cf <- units()
    
    df2 <- with(df_ngf,df_ngf[(df$year >= yrs[1] & df$year <= yrs[length(yrs)]),]) # only for full years of data
    
    data.diurnal <- df2 %>%
      mutate(
        year = as.factor(year(datetime)),
        month = month(datetime),
        day = day(datetime),
        jday = yday(datetime),
        hour = hour(datetime),
        minute = minute(datetime),
        HHMM = format(as.POSIXct(datetime), format = "%H:%M")
      ) %>%  # Create hour and minute variable (HHMM)
      group_by(year, HHMM) %>%
      dplyr::summarize(var = median(var,na.rm = TRUE))
    
    data.diurnal$time <- as.POSIXct(as.character(data.diurnal$HHMM), format="%R", tz="UTC")
    
    p <- ggplot() +
      geom_line(data = data.diurnal, aes(x = time, y = var,color = year)) +
      scale_x_datetime(breaks="6 hours", date_labels = "%R") + ylab(paste0(var_in[[1]][1]," (",units_cf,")",sep = ""))
    
    p <- ggplotly(p) %>% toWebGL()
    p
    
  })
}
```

# Flux diagnostics

## Column {data-width="600"}

### Flux diagnostics

```{r}
flux_diagnostic_plots(data,vars_flux_diag_signal_strength,vars_flux_diag_records,vars_flux_diag_flowrate)
```

## Column {data-width="400"}

### EBC half-hourly

```{r}
scatter_plot_QCQA_EBC(data_thirdstage,vars_EBC_AE,c("H","LE"),"AE  (W m-2)","H+LE (W m-2)")
```

### EBC daily

```{r}
scatter_plot_QCQA_EBC_daily(data_thirdstage,vars_EBC_AE,c("H","LE"),"AE  (W m-2)","H+LE (W m-2)")
```
